\chapter*{Acknowledgements}
\label{chap:ack}
\addcontentsline{toc}{chapter}{Acknowledgements}

\vspace{4ex}
First and above all, I give thanks to the Creator and Engineer of all the universe, the One who made 
this all possible and that granted me the capability to proceed successfully. 
This thesis appears in its current form due to the assistance and guidance of several people. 
I would therefore like to offer my sincere thanks to all of them.
I offer my deepest gratitude to the assistant supervisor of this thesis and
coworker of the research project object of this thesis, Ph.D student Marco Driusso, whose expertise, 
understanding, and patience, was fundamental for the outcome of the research project. Moreover, I appreciate 
his vast knowledge and skills in many areas, and his assistance  in writing and refine this thesis.
I have to appreciate the guidance of the head of the project and supervisor of this thesis, Prof.~Fulvio 
Babich whose has guided the team in achieving the goal. 
Moreover, I would like to thank Dr.~Chris Marshall from u-blox LTD, who guided all the team of the 
Telecommunications Group in Trieste through the exciting and challenging project of positioning with 
LTE signals.
I acknowledge my gratitude to the team of \acrfull{hsr}, who gave us access to their acquired LTE data 
and simulation software.  
My very sincere thanks goes to Dr.~Christian Gentner of the \acrfull{dlr} who provided us the LTE 
emulated signals realized with an agreement with Rohde \& Schwarz, that was essential for 
the validation of the developed frameworks.
Last, but not least, many thanks to Prof.~Massimiliano Comisso, member of the Telecommunication research team,  
that was always willing and helpful in our research work.
Finally, I take this opportunity to express the profound gratitude to my beloved parents, 
my grandmother, and my friends for their love and continuous support, both spiritually and materially.